\documentclass{amsart}

\input{StandardPaper2.tex}

\begin{document}

\title[Harnack and Type II Classification]
 {Harnack estimates for non-collapsing and classification of Type II singularities for Mean Curvature Flow}

\curraddr{}
\email{}
\date{\today}

\dedicatory{}
\subjclass[2010]{}
\keywords{}

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}

\begin{enumerate}
\item Hamilton's Harnack implies Type II singularities blow up to translating solitons. Can also split out all lines to obtain $\R^k \times M^{n-k}$ with $M^{n-k}$ strictly convex. Is it also compact? ref? The conjecture is that $M^{n-k}$ is rotationally symmetric. 
\item To pick up rotational symmetry, use the non-collapsing two-point function $k(x,y)$. If we can prove a Harnack inequality for this, with equality occurring precisely on rotationally symmetric solitons, then similar arguments above for the translating solitons might prove the conjecture!
\end{enumerate}

\section{Preliminaries}

\begin{enumerate}
\item Describe the non-collapsing quantity.
\item Describe notation.
\item Describe translating graphs.
\item For translating graphs we can calculate easily $k(x,y)$ and it constant in time, $\partial_t k = 0$. Transforming to the mean curvature flow parametrisation we then will obtain $\partial_t k + A = 0$ for some quantity $A$. See Ben Andrews change from Gauss parametrisation to mean curvature flow parametrisation. This will give us the quantity
\[
\chi = t(\partial_t k + A) + \delta k
\]
as the basic Harnack quadratic to study.
\item The change of parametrisation is easily obtained. If our translating graph is given by $U(x,t) = (x,t + u(x))$ for $u : \R^n \to \R$, then we just define
\[
F(x,t) = U(f_t(x), t) = (f_t(x), t + u(f_t(x)))
\]
where $f_t : \R^n \to \R^n$ is a one-parameter subgroup of diffeomorhphisms satisfying
\[
\partial_t f_t = \frac{\grad u}{1 + |\grad u|^2}.
\]
\item Question: If we have a translator that is a graph over some hyperplane, is it necessarily true that it is a graph over the hyperplane orthogonal to the translation direction. I suspect yes, but haven't checked.
\item Another way to derive $A$ could be to follow Hamilton and differentiate the soliton equation. However, this won't bring out the non-collapsing quantity so this may approach may not lead anywhere, i.e. it just recovers the Harnack inequality for the speed. Perhaps there is some way to express $k$ using the soliton equation however, and then differentiate that?
\end{enumerate}

\section{Evolution equations}

\begin{enumerate}
\item Calculate evolution of $\chi$. Here be dragons.
\end{enumerate}

\section{The Harnack Inequality}

\begin{enumerate}
\item Apply the maximum principle to obtain the Harnack inequality.
\end{enumerate}

\section{Classification of Type II singularities}

\begin{enumerate}
\item Show that equality is attained only for rotationally symmetric translators.
\item Show that the blow up limit must satisfy equality in our Harnack for $k$.
\item Classification. Boom!
\end{enumerate}

\bibliographystyle{amsplain}
\bibliography{Bibliography.bib}


\end{document}
